Clustering time series based on probability distributions across temporal granularities

### 2021-11-16 main.Rmd
Fig 9 update

df = tibble::tibble(scenario, " \\# designs" = designs, niter,  "$\\mu$" = mu, nT) %>%
  knitr::kable(format = "latex",
             escape = FALSE,
             caption = "The range of parameters used for the validation study, for the three different scenarios, number of simulations ($niter$) for each design, differences between means ($\\mu$) across granularities and series lengths ($nT$).")%>%
  kableExtra::collapse_rows(columns = 3:5)

@@

The $sindex$ is plotted against the number of clusters for clustering based on JS-based (JS-NQT) distances in Figure \ref{fig:opt-cluster-tsne-jsd}. The $sindex$ falls from around $0.56$ when $k=3$ to $0.54$ when $k$ increases. In our study, we use $k=4, 5$. Figure \ref{fig:groups-4and5} depicts the summarized distributions across $4$ and  $5$ clusters in (a) and (b) respectively, and assists in characterizing each cluster. A-2, Groups A-3, and A-4 have profiles that correspond to B-2, B-3, and B-5, respectively. B-2 (id: 4-9 in Figure \ref{fig:hod-ind-group-png}) and B-5 (id: 21-24) have a `hod` pattern with a typical morning and evening peak, whereas the other groups have no distinct pattern or high variability throughout the day. A-1 is subdivided into B-1 and B-4, each of which has a distinct shape across `moy` and `wnwd`. B-4 (id: 16-20) is distinguished by higher energy consumption in the first few months of the year and greater variability in weekend usage. B-1 (id: 1-3) has higher consumption in the middle of the year (winter months) and a similar weekday-weekend inter-quartile range. When $k = 4$ is used, these two groups merge to form A-1, which has a moy profile of higher usage in both the beginning and middle of the year, which is not representative of the individuals. It may be worthwhile to compare Figures \ref{fig:opt-cluster-tsne-jsd} and \ref{fig:hod-ind-group-png} to see if the summarized distributions across groups accurately characterized the groupings. If it has, then the majority of the members of the group should have a similar profile.

@@

```{r groups-4and5, fig.cap = "For $k = 4$ (a) and $k=5$ (b), the distribution of electricity demand across groups over hod, moy, and wnwd is shown. Groups A-2, A-3, and A-4 profiles correspond to Groups B-2, B-3, and B-5, respectively. A-1 is split into B-1 and B-4, each of which has a distinct shape across moy and wnwd. B-4 (id: 16-20) is characterized by higher energy consumption in the first few months of the year and more variation in weekend usage. B-1 (id:1-3) is distinguished by higher consumption in the middle of the year (winter months) and similar weekday-weekend inter-quartile range. When $k = 4$ is used, these two groups merge to form A-1, which has a moy profile of higher usage in both the beginning and middle of the year, which is not representative of the individuals in the group.", fig.height=6}

>>>>

df = tibble::tibble(scenario, " designs" = designs, niter,  "$\\mu$" = mu, nT) %>%
  knitr::kable(format = "latex",
             escape = FALSE,
             caption = "The range of parameters used for the validation study, for the three different scenarios, number of simulations ($niter$) for each design, differences between means ($\\mu$) across granularities and series lengths ($nT$).")%>%
  kableExtra::collapse_rows(columns = 3:5)

@@

The $sindex$ is plotted against the number of clusters for clustering based on JS-based (JS-NQT) distances in Figure \ref{fig:opt-cluster-tsne-jsd}. The $sindex$ falls from around $0.56$ when $k=3$ to $0.54$ when $k$ increases. In our study, we use $k=4, 5$. Figure \ref{fig:groups-4and5} depicts the summarized distributions across $4$ and $5$ clusters in (a) and (b) respectively, and assists in characterizing each cluster. A-1, Groups A-2, and A-3 have profiles that correspond to B-1, B-2, and B-3, respectively. B-2 (id: 4-9 in Figure \ref{fig:hod-ind-group-png}) and B-1 (id: 21-24) have a `hod` pattern with a typical morning and evening peak, whereas the other groups have no distinct pattern or high variability throughout the day. A-4 is subdivided into B-4 and B-5, each of which has a distinct shape across `moy` and `wnwd`. B-4 (id: 16-20) is distinguished by higher energy consumption in the first few months of the year and greater variability in weekend usage. B-5 (id: 1-3) has higher consumption in the middle of the year (winter months) and a similar weekday-weekend inter-quartile range. When $k = 4$ is used, these two groups merge to form A-4, which has a moy profile of higher usage in both the beginning and middle of the year, which is not representative of the individuals. It may be worthwhile to compare Figures \ref{fig:opt-cluster-tsne-jsd} and \ref{fig:hod-ind-group-png} to see if the summarized distributions across groups accurately characterized the groupings. If it has, then the majority of the members of the group should have a similar profile.

@@

```{r groups-4and5, fig.cap = "For $k = 4$ (a) and $k=5$ (b), the distribution of electricity demand across groups over hod, moy, and wnwd is shown. Groups A-1, A-2, and A-3 profiles correspond to Groups B-1, B-2, and B-3, respectively. A-4 is split into B-4 and B-5, each of which has a distinct shape across moy and wnwd. B-4 (id: 16-20) is characterized by higher energy consumption in the first few months of the year and more variation in weekend usage. B-5 (id:1-3) is distinguished by higher consumption in the middle of the year (winter months) and similar weekday-weekend inter-quartile range. When $k = 4$ is used, these two groups merge to form A-4, which has a moy profile of higher usage in both the beginning and middle of the year, which is not representative of the individuals in the group.", fig.height=5}
